Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-09-18 paper/paper.Rmd
clarify the term blocking again

The terminology "block" used in this categorization and in the manuscript in general refers to any kind of regular and irregularly shaped grouping of observations and not necessarily only to a rectangular partitioning as used in some methods.

>>>>

The terminology "block" used in this categorization and in the manuscript in general refers to any kind of regular and irregularly shaped grouping of observations which divides the study area into different zones [russ2010; @bahn2012; @wenger2012].
This is different to the meaning of rectangular-only partitioning within some specific resampling methods [@blockCV].
